Distributed Version Control Systems

### 2010-05-16 paper.tex
movida seccion para la parte de conclusiones
Reescrita la primer oración de Peer code review

\subsection{Peer code review}
If doing code review is a common practice, then using a DVCS can aid to this process. Since changes can be shared
among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be
working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the
reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
This also prevented them from sharing the code through a public repository, which can present some disadvantages like
a third developer using code that is not yet intended for general use.

>>>>

\subsection{Peer code review}
Using a DCVS can help isolate the code review between both developers without disrupting the rest of the team.
Since changes can be shared among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the reviewer can just clone the reviewee's repository and can have it separately from its current changes.
This also prevented them from sharing the code through a public repository, which can present some disadvantages like a third developer using code that is not yet intended for general use.
